Sending a Balloon to the Edge of Space

### 2018-11-14 paper/paper.rmd
changed appendix reference
changed appendix reference for schematic
edit temp. errorbarrs

The circuit consists of two Arduinos, one Mega ATK and one Uno. The Mega ATK is our primary microcontroller and controls the logger, transmitter, and receives input from every sensor except for the accelerometer. The accelerometer and another microSD logger are the only two components on the secondary Arduino Uno. The reason for the accelerometer needing it’s own Arduino is because the $I^2C$ library it required was not compatible with the other devices running on $I^2C$, such as the BME280 and spectrometer. The primary Arduino is powered by three batteries, and one battery powers the secondary arduino and the methane sensor. The methane sensor uses a large amount of power so it is with the secondary Arduino’s power supply so that if the sensor uses too much power it will not disrupt the majority of the data collection and sensors. All batteries go through 1 Amp 5 Volt voltage regulators, one for the primary Arduino and one for the secondary Arduino and methane sensor. The built in voltage regulator on the Arduino was not powerful enough and causing the sensors to malfunction so exterior regulators were included. Every sensor connects individually to either an analog pin or digital pin, or is one of the three sensors that connect to the SDA and SCL pins. See Appendix for schematic.

@@

The data acquisition organization for the microcontroller consists of the main arduino .ino file calling methods in different header files to get data for an array. Every loop, the data array is filled with the current time, GPS coordinates, pressure, and more sensor data (See Appendix V for full data index). The sensors are grouped into three header files, one for the four individual experiments using analog sensors, one for the BME280 exterior humidity and temperature sensor, and one for the clock, GPS, interior temperature, and pressure sensors. The GPS sensor uses Serial UART to send the coordinates of the antenna. Additionally, all of the getter methods for sensors like GPS check to make sure that if the sensor fails, the method will still return a value so that the Arduino can continue to get the rest of the data.

@@

pv$upper_temp_error = sapply(pv$temp_recal, function(x) x + 0.014598 * x)
pv$lower_temp_error = sapply(pv$temp_recal, function(x) x - 0.014598 * x)

a <- ggplot(pv, aes(x=height, y=temp_recal)) + geom_point(aes(color="Measured Inside")) + 
  geom_point(aes(y=cTemp, color="Calculated Outside")) + 
  scale_color_manual("Temperature", breaks=c("Measured Inside", "Calculated Outside"),
                        values=c("black", "purple")) + 
  theme(legend.position = c(0.7, 0.9)) + labs(title="Calculated External and Measured Internal Temperature\n vs. Height",
                                        x="Height (m)", y="Temperature (C)") +
  geom_errorbar(data=pv, aes(x=height, ymin=lower_temp_error, ymax=upper_temp_error))
a
```
Figure 15

>>>>

The circuit consists of two Arduinos, one Mega ATK and one Uno. The Mega ATK is our primary microcontroller and controls the logger, transmitter, and receives input from every sensor except for the accelerometer. The accelerometer and another microSD logger are the only two components on the secondary Arduino Uno. The reason for the accelerometer needing it’s own Arduino is because the $I^2C$ library it required was not compatible with the other devices running on $I^2C$, such as the BME280 and spectrometer. The primary Arduino is powered by three batteries, and one battery powers the secondary arduino and the methane sensor. The methane sensor uses a large amount of power so it is with the secondary Arduino’s power supply so that if the sensor uses too much power it will not disrupt the majority of the data collection and sensors. All batteries go through 1 Amp 5 Volt voltage regulators, one for the primary Arduino and one for the secondary Arduino and methane sensor. The built in voltage regulator on the Arduino was not powerful enough and causing the sensors to malfunction so exterior regulators were included. Every sensor connects individually to either an analog pin or digital pin, or is one of the three sensors that connect to the SDA and SCL pins. See Appendix VIII for schematic.

@@

The data acquisition organization for the microcontroller consists of the main arduino .ino file calling methods in different header files to get data for an array. Every loop, the data array is filled with the current time, GPS coordinates, pressure, and more sensor data (See Appendix IX for full data index). The sensors are grouped into three header files, one for the four individual experiments using analog sensors, one for the BME280 exterior humidity and temperature sensor, and one for the clock, GPS, interior temperature, and pressure sensors. The GPS sensor uses Serial UART to send the coordinates of the antenna. Additionally, all of the getter methods for sensors like GPS check to make sure that if the sensor fails, the method will still return a value so that the Arduino can continue to get the rest of the data.

@@

pv$upper_temp_error = sapply(pv$temp_recal, function(x) x + 8.49)
pv$lower_temp_error = sapply(pv$temp_recal, function(x) x - 8.49)

a <- ggplot(pv, aes(x=height, y=temp_recal)) + geom_errorbar(data=pv, aes(x=height, ymin=lower_temp_error, ymax=upper_temp_error, color="Thermistor Error: 8.49 °C")) + 
geom_point(aes(x=height, y=temp_recal, color="Measured Inside")) + 
  geom_point(aes(y=cTemp, color="Calculated Outside")) + 
  scale_color_manual("Temperature", breaks=c("Measured Inside", "Calculated Outside", "Thermistor Error: 8.49 °C"),
                        values=c("black", "purple", "darkblue")) + 
  theme(legend.position = c(0.7, 0.8)) + labs(title="Calculated External and Measured Internal Temperature\n vs. Height",
                                        x="Height (m)", y="Temperature (C)")
a
```
Figure 15
